Annotated example of index standardization with VAST

### 2021-11-24 doc/appendix-pcod-VAST.Rmd
make effort variable numeric

```{r fit, echo = TRUE, results = 'hide'}
dir.create(paste0(here::here("doc", "appendix-VAST"))) # create folder for saved output

pcod$effort = 1 # effort is 1 when using CPUE instead of observed weight as the response

>>>>

```{r fit, echo = TRUE, results = 'hide'}
dir.create(paste0(here::here("doc", "appendix-VAST")), showWarnings = FALSE) # create folder for saved output

pcod$effort <- as.numeric(1) # effort is 1 when using CPUE instead of observed weight as the response
